Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-31 forecast/paper/paper.tex
Start supplement copyedits

However, rigorously vetting the details for more sophisticated models, as well
as the generalizability of our findings to different geographic resolutions,
both remain important directions for future study.  For example, in the
Supplementary Materials we show that for forecasting at the state level, the
benefits provided by indicators models over AR are generally less clear
(compared to those observed at the HRR level).  One hypothesis is that at the
state level, where the signal-to-noise ratio (SNR) is higher, AR performs even
better and provides a higher standard (when asking whether it can be improved
upon using indicators).  At the HRR level, where the SNR is lower, including the
indicators as additional linear features in the AR model likely serves as an
important variance reduction (just like averaging independent terms would) which
contributes to improved accuracy.  But at a higher SNR, this variance
reduction becomes less important, and we may be compelled to use more
sophisticated modeling techniques to extract comparable value from the
indicators.

>>>>

However, rigorously vetting the details for more sophisticated models, as well
as the generalizability of our findings to different geographic resolutions,
both remain important directions for future study.  For example, in the
Supplementary Materials we show that for forecasting at the state level, the
benefits provided by indicators models over AR are generally less clear
(compared to those observed at the HRR level).  One hypothesis is that at the
state level, where the signal-to-noise ratio (SNR) is higher, AR performs even
better and provides a higher standard (when asking whether it can be improved
upon using indicators).  At the HRR level, where the SNR is lower, including the
indicators as additional linear features in the AR model probably delivers a
kind of variance reduction (just like averaging independent terms would) which 
contributes to improved accuracy.  But at a higher SNR, this variance
reduction becomes less important, and we may be compelled to use more
sophisticated modeling techniques to extract comparable value from the
indicators.

### 2021-10-31 forecast/paper/supplement-text.tex
Start supplement copyedits

\chngcli~(and, to a lesser extent, the other claims-based signals) is the most
affected by this distinction, reflecting the latency in claims-based reporting.
This underscores the importance of efforts to provide ``nowcasts'' for claims
signals (which corresponds to a 0-ahead forecast of what the claims signal's
value will be once all data has been collected). Looking at the \chngcli~and
\dv~curves in Figure \ref{fig:fcast-finalized}, we can see that they perform
very similarly when trained on the finalized data.  This is reassuring because
they are, in principle, measuring the same thing (namely, the percentage of
outpatient visits that are primarily about COVID-related symptoms).  The
substantial difference in their curves in Figure 3 of the main paper must
therefore reflect their having very different backfill profiles.

While using finalized rather than vintage data affects \dv~the least for
forecasting, it is one of the most affected methods for the hotspot problem.
This is a reminder that the forecasting and hotspot problems are fundamentally
distinct.  For example, the hotspot problem does not measure the ability to
distinguish between flat and downward trends.

Even the \ar~model is affected by this distinction, reflecting the fact that the
case rates themselves (i.e., the response values) are also subject to revision.
The forecasters based on indicators are thus affected both by revisions to the
indicators and by revisions to the case rates.  In the case of the \gs~model, in
which we only used finalized values for the \gs~indicator, the difference in
performance can be wholly attributed to revisions of case rates.

>>>>

\chngcli~(and, to a lesser extent, the other claims-based signals) is the most
affected by this distinction, reflecting the latency in claims-based reporting.
This underscores the importance of efforts to provide ``nowcasts'' for claims
signals (which corresponds to a 0-ahead forecast of what the claims signal's
value will be once all data has been collected). Looking at the \chngcli~and
\dv~curves in Figure \ref{fig:fcast-finalized}, we can see that they perform
very similarly when trained on the finalized data.  This is reassuring because
they are, in principle, measuring the same thing (namely, the percentage of
outpatient visits that are primarily about COVID-related symptoms), but based on
data from different providers.  The substantial difference in their curves in
Figure 3 of the main paper must therefore reflect their having very different
backfill profiles.

While using finalized rather than vintage data affects \dv~the least for
forecasting, it is one of the most affected methods for the hotspot problem.
This is a reminder that the forecasting and hotspot problems are fundamentally
different problems.  For example, the hotspot problem does not measure the
ability to distinguish between flat and downward trends.

Even the \ar~model is affected by this distinction, reflecting the fact that the
case rates themselves (i.e., the response values) are also subject to revision.
The forecasters based on indicators are thus affected both by revisions to the
indicators and by revisions to the case rates.  And in the case of the
\gs~model, in which we only used finalized values for the \gs~indicator, the
difference in performance can be wholly attributed to revisions of case rates.

### 2021-10-31 forecast/paper/supplement.Rmd
Start supplement copyedits

```{r fcast-honest-v-finalized, fig.cap="Relative forecast WIS with vintage compared to finalized data. Using finalized data leads to overly optimistic performance."}
plotter(
  left_join(
    fcasts_honest %>% select(forecaster:wis),
    fcasts_finalized %>% select(forecaster:wis) %>%
      rename(finalized_wis = wis)
    ), 
  "wis", Mean, scaler = "finalized_wis", 
  order_of_operations = c("aggr","scale")) +
  geom_hline(yintercept = 1) +
  ylab("Mean WIS (vintage / finalized)")

@@

ggplot(st, aes(p)) +
  geom_histogram(
    aes(y = after_stat(density), color = forecaster, fill = forecaster), 
    alpha = 0.4,
    bins = 40) +
  scale_color_manual(values = fcast_colors2, guide = guide_legend(nrow = 1)) +
  scale_fill_manual(values = fcast_colors2, guide = guide_legend(nrow = 1)) +
  facet_wrap(~forecaster) +
  ylab("Frequency") +
  xlab("P-value") +
  scale_y_continuous(
    labels = scales::percent_format(scale = 1, accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "bottom")

>>>>

```{r fcast-honest-v-finalized, fig.cap="Relative forecast WIS with vintage compared to finalized data. Using finalized data leads to overly optimistic performance."}
plotter(
  left_join(
    fcasts_honest %>% select(forecaster:wis),
    fcasts_finalized %>% select(forecaster:wis) %>%
      rename(finalized_wis = wis)
    ), 
  "wis", Mean, scaler = "finalized_wis", 
  order_of_operations = c("aggr","scale")) +
  geom_hline(yintercept = 1) +
  ylab("Mean WIS (vintage / finalized)")
```

@@

ggplot(st, aes(p)) +
  geom_histogram(
    aes(y = after_stat(density), color = forecaster, fill = forecaster), 
    alpha = 0.4,
    bins = 40) +
  scale_color_manual(values = fcast_colors2, guide = guide_legend(nrow = 1)) +
  scale_fill_manual(values = fcast_colors2, guide = guide_legend(nrow = 1)) +
  facet_wrap(~forecaster) +
  ylab("Frequency") +
  xlab("P-value") +
  scale_y_continuous(
    labels = scales::percent_format(scale = 1, accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "bottom")
```
